Hydra Battles and Cie

### 2021-08-12 doc/part-hydras.tex
converting chapter 4 to Alectryon (start)
converting chapter 4 to Alectryon

First, we declare a notation scope for \texttt{E0}.

\begin{Coqsrc}
Declare Scope E0_scope.
Delimit Scope E0_scope with e0.
Open Scope E0_scope.
\end{Coqsrc}

Then we redefine the predicates of comparison.

\label{Predicates:Lt-E0}

\begin{Coqsrc}
Definition Lt (alpha beta : E0) := T1.LT (@cnf alpha) (@cnf beta).
Definition Le (alpha beta : E0) := T1.LE (@cnf alpha) (@cnf beta).

Infix "o<" := Lt : E0_scope.
Infix "o<=" := Le : E0_scope.
\end{Coqsrc}

@@

\begin{Coqsrc}
Require Import Logic.Eqdep_dec.

Lemma nf_proof_unicity :
  forall (alpha:T1) (H H': nf alpha), H = H'.

Lemma E0_eq_iff alpha beta : alpha = beta <-> cnf alpha = cnf beta.
\end{Coqsrc}

\index{hydras}{Exercises}
\begin{exercise}
In earlier versions of this development, the predicate \texttt{nf} was defined  inductively, with various constructors describing all possible cases.
\begin{enumerate}
\item Please give such a definition, in a dedicated module.
\item Prove the logical equivalence between your definition and ours.
\item Define a variant of the type \texttt{E0} (with your definition of \texttt{nf}).
\item Can you still prove a lemma like \texttt{E0\_eq\_iff} ? With the help of an axiom from some module of the standard library ?
\end{enumerate}
\end{exercise}

@@

\label{sect:omega-T1}
%\index{Constants!zero:T1}

\begin{Coqsrc}
Instance Zero : E0.
Proof.
  now exists T1.zero.
Defined.

Instance _Omega : E0.
Proof.  now exists omega%t1. 
Defined.

Notation omega  := _Omega.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint succb (alpha:T1) : bool :=
  match alpha with
    | zero => false
    | ocons zero _ _ => true
    | ocons alpha n beta => succb beta
  end.

Fixpoint limitb (alpha : T1) : bool :=
  match alpha with
    | zero => false
    | ocons zero _ _ => false
    | ocons alpha n zero => true
    | ocons alpha n beta => limitb beta
  end.
\end{Coqsrc}

\begin{Coqsrc}
  Compute limitb omega.
\end{Coqsrc}

\begin{Coqsrc}
Compute succb 42.
\end{Coqsrc}

@@

   The following function is very useful in constructions by cases (proofs and function definitions).

\begin{Coqsrc}
Definition zero_succ_limit (alpha: T1) :
    {succb alpha} + {limitb alpha} +  {alpha=zero}.
    (* ... *)
Defined.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint succ (alpha:T1) : T1 :=
  match alpha with 
   | zero => 1
   | ocons zero n _ => ocons zero (S n) zero
   | ocons beta n gamma => ocons beta n (succ gamma)
 end.
\end{Coqsrc}

@@

\begin{Coqsrc}
 Lemma succb_iff alpha (Halpha : nf alpha) :
  succb alpha <-> exists beta : T1, nf beta /\ alpha = succ  beta.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint plus (alpha beta : T1) : T1 :=
  match alpha,beta with
 |  zero, y  => y
 |  x, zero  => x
 |  ocons a n b, ocons a' n' b' =>
    (match compare a a' with
     | Lt => ocons a' n' b'
     | Gt => (ocons a n (plus b (ocons a' n' b')))
     | Eq  => (ocons a (S(n+n')) b')
     end)
  end
where "alpha + beta" := (plus alpha beta) : t1_scope.
\end{Coqsrc}

\begin{Coqsrc}
Fixpoint mult (alpha beta : T1) :T1 :=
  match alpha,beta with
 |  zero, y  => zero
 |  x, zero => zero
 |  ocons zero n _, ocons zero n' _ => 
                 ocons zero (Peano.pred((S n) * (S n'))) zero
 |  ocons a n b, ocons zero n' b' =>  
                 ocons a (Peano.pred((S n) * (S n'))) b
 |  ocons a n b, ocons a' n' b' =>
     ocons (a + a') n' ((ocons a n b) * b')
 end
where  "alpha * beta" := (mult alpha beta) : t1_scope.
\end{Coqsrc}

@@

\begin{Coqsrc}
Example e2 : 6 + omega = omega.
Proof. reflexivity. Qed.

Example e'2 : omega t1< omega + 6.
Proof. now compute. Qed.

Example e''2 : 6 * omega = omega.
Proof. reflexivity. Qed.

Example e'''2 : omega t1< omega * 6.
Proof. now compute. Qed.
\end{Coqsrc}

>>>>

\input{movies/snippets/E0/LtLeDef}

@@

\input{movies/snippets/E0/nfProofUnicity}

\input{movies/snippets/E0/E0EqIff}

@@

\label{sect:omega-T1}

\input{movies/snippets/E0/ZeroOmegaDef}

@@

\input{movies/snippets/T1/succbLimitb}

@@

@@

\input{movies/snippets/T1/succDef}

@@

\input{movies/snippets/T1/succbIff}

@@

\input{movies/snippets/T1/plusDef}

\input{movies/snippets/T1/multDef}

@@

\input{movies/snippets/T1/plusMultExamples}
